$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-01-31 paper/e6ssm-tuning-paper.tex
Updated general U(1) plots, updated caption in the corresponding figure (which may be a bit awkwardly written, might consider rewriting), and changed occurrences of \it to \textit

\begin{figure}[h]
\begin{center}
\resizebox{!}{6.1cm}{%
\includegraphics{mssm_stop_tuning.png}}
\resizebox{!}{6.1cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{{\it Left panel:} Scatter plot of fine tuning in the MSSM as a function of
the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
{\it Right panel:} Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cutoff scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmstoptuning}
\end{center}
\end{figure}
To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
we show the variation in fine tuning when we scan over the stop masses
and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq
10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{
  GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.  The remaining
parameters we fix such that at $M_{\rm SUSY}$ they have the values
$\mu=-97.5$ GeV, $B=-84.8$ GeV, $M_1=92.1$ GeV, $M_2=95.9$ GeV,
$M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV,
$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and
$m_{d_i}=438$ GeV ($i=1,2,3$). Although we should stress that making
this choice will lead to a spectrum which is in conflict with the LHC
limits, doing so ensures that fine tuning due to the other parameters
is small, so that we avoid washing out the fine tuning impact of the
stops when the tuning is small\footnote{For models in which the
  spectrum is heavier, when the stop masses are small the fine tuning
  reaches a lower bound imposed by other heavier parameters.} as can
be the case when the stop masses are less than 1 TeV.  Note that the
Higgs mass is also allowed to vary in this scan, as shown in the right
panel of Fig.~\ref{Fig:mssmstoptuning}. This illustrates the tuning
problem which people have been worrying about since the discovery of
the 125 GeV Higgs boson as we see that raising the stop masses is also
pushing up the Higgs mass, meaning that heavier Higgs masses require
more fine tuning.  However for a low value of the UV scale this tuning
is not so severe unless the stops are very heavy, and a 125 GeV Higgs
can be obtained without much tuning in this unrealistic case where we
have minimised other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cutoff such that for $M_X =
10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
tuning of $\approx 100 - 1000$ and the minimum tuning we see consistent
with a $125$ GeV Higgs is $\approx 200$, as shown in
Fig.~\ref{Fig:mssmstoptuning}.

@@

\begin{figure}
\begin{center}
\resizebox{!}{5cm}{%
\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
\resizebox{!}{5cm}{%
\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
\resizebox{!}{5cm}{%
\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}%%
\caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue
(bottom band) and $M_{Z^\prime} = 4.5$ TeV in red (top band).}
\label{Fig:othere6modelsvsmssm}
\end{center}
\end{figure}

@@

\caption{{\it Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}. {\it Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel. {\it Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel. {\it Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel. {\it Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.    }

>>>>

\begin{figure}[h]
\begin{center}
\resizebox{!}{6.1cm}{%
\includegraphics{mssm_stop_tuning.png}}
\resizebox{!}{6.1cm}{%
\includegraphics{mssm_higgs_tuning.png}}
\caption{\textit{Left panel:} Scatter plot of fine tuning in the MSSM as a function of
the lightest stop mass, $m_{\tilde{t}_1}$, for the cutoff scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV. 
\textit{Right panel:} Scatter plot of fine tuning in the MSSM as a function of
the lightest Higgs mass, $m_{h_1}$, for the cutoff scales (from 
bottom to top) $M_X=20$ TeV, $M_X=50$ TeV, $M_X=100$ TeV and $M_X=10^{16}$ GeV.}
\label{Fig:mssmstoptuning}
\end{center}
\end{figure}
To illustrate this, in the left panel of Fig.~\ref{Fig:mssmstoptuning}
we show the variation in fine tuning when we scan over the stop masses
and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq
10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{
  GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV.  The remaining
parameters we fix such that at $M_{\rm SUSY}$ they have the values
$\mu=-97.5$ GeV, $B=-84.8$ GeV, $M_1=92.1$ GeV, $M_2=95.9$ GeV,
$M_3=352$ GeV, $A_b=-117.9$ GeV, $A_\tau=-7.8$ GeV, $m_{L_i}=400$ GeV,
$m_{e_i}=204$ GeV, $m_{Q_{1,2}}=438$ GeV, $m_{u_{1,2}}436$ GeV and
$m_{d_i}=438$ GeV ($i=1,2,3$). Although we should stress that making
this choice will lead to a spectrum which is in conflict with the LHC
limits, doing so ensures that fine tuning due to the other parameters
is small, so that we avoid washing out the fine tuning impact of the
stops when the tuning is small\footnote{For models in which the
  spectrum is heavier, when the stop masses are small the fine tuning
  reaches a lower bound imposed by other heavier parameters.} as can
be the case when the stop masses are less than 1 TeV.  Note that the
Higgs mass is also allowed to vary in this scan, as shown in the right
panel of Fig.~\ref{Fig:mssmstoptuning}. This illustrates the tuning
problem which people have been worrying about since the discovery of
the 125 GeV Higgs boson as we see that raising the stop masses is also
pushing up the Higgs mass, meaning that heavier Higgs masses require
more fine tuning.  However for a low value of the UV scale this tuning
is not so severe unless the stops are very heavy, and a 125 GeV Higgs
can be obtained without much tuning in this unrealistic case where we
have minimised other sources of tuning.  On the other hand the tuning
becomes more severe as we increase the cutoff such that for $M_X =
10^{16}$ GeV a lightest stop masses of $1-3$ TeV can result in a fine
tuning of $\approx 100 - 1000$ and the minimum tuning we see consistent
with a $125$ GeV Higgs is $\approx 200$, as shown in
Fig.~\ref{Fig:mssmstoptuning}.

@@

\begin{figure}
\begin{center}
\resizebox{!}{6.1cm}{%
\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
\resizebox{!}{6.1cm}{%
\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
\resizebox{!}{6.1cm}{%
\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}%%
\caption{\textit{Top left panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_I$ model. \textit{Top right panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\psi$ model. \textit{Bottom panel:} Scatter plot of the fine tuning vs lightest Higgs mass in the $U(1)_\eta$ model. In each plot points with $M_{Z^\prime} = 2.5$ TeV are shown in blue
(bottom band), and points with $M_{Z^\prime} = 4.5$ TeV are shown in red (top band).}
\label{Fig:othere6modelsvsmssm}
\end{center}
\end{figure}

@@

\caption{\textit{Top panel:} Scatter plot of the fine tuning as a function of the cutoff scale $M_X$ for the four benchmark points given in Table \ref{tab:benchmarks}. \textit{Middle left panel:}  Individual sensitivities for MSSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the green line in the top panel. \textit{Middle right panel:} Individual sensitivities for E$_6$SSM BM1 plotted against the high scale $M_X$ which give the overall tuning shown by the blue line in the top panel. \textit{Bottom left panel:} Individual sensitivities for MSSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the yellow line in the top panel. \textit{Bottom right panel:} Individual sensitivities for E$_6$SSM BM2 plotted against the high scale $M_X$ which give the overall tuning shown by the red line in the top panel.    }
